---
title: "R Notebook"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---


1 - Calling ISLR library and printing the summary of Carseats dataset
```{r}
library(ISLR)
s<-Carseats#assigning the Carseats dataset to a variable
print(summary(s))
```

2 - Printing the number of rows in the dataset
```{r}
print(paste("Number of rows in the dataset are:",nrow(s)))

print(paste("Maximum value of Advertising is:", max(s$Advertising)))#calculating the maximum value of the Advertising column
```
3 - Calculating Interquartile Range (IQR)
```{r}
print(paste("The Inter Quartile Range of Price is:", IQR(s$Price)))
```
4 - Plotting Price vs Sales

```{r}
library(tidyverse)
library(car)
scatterplot(Price ~ Sales, data=s)

cor(s$Price,s$Sales,method='pearson')#calculating the correaltion between Price and Sales
```
Here, from the plot we notice that, as the Price of the Carseats are increasing the sales are decreasing.\
From the above we calculated the correlation of Price and Sales of the Carseats. We notice that the correlation between the two is a negative linear correlation.
